Motmot: A Distributed Chat Protocol

### 2012-05-04 paper/paper.tex
Fixing bib
Bluh bloh blah
More paper
No
Bloof
libmotmot intro and more bibses

@@

\title{Motmot: A Secure, Distributed Chat Service}

\numberofauthors{5}
%
\author{
\alignauthor
Carl Jackson \\
  \affaddr{Harvard University} \\
  \email{cjackson@college.harvard.edu}
%
\alignauthor
Max Wang \\
  \affaddr{Harvard University} \\
  \email{max.wang@college.harvard.edu}
%
\and
\alignauthor
EJ Bensing \\
  \affaddr{Harvard University} \\
  \email{ebensing@college.harvard.edu}
%
\alignauthor
Jeff Atwood \\
  \affaddr{Harvard University} \\
  \email{jatwood@college.harvard.edu}
%
\alignauthor
Julie Hansbrough \\
  \affaddr{Harvard University} \\
  \email{jhansbrough@college.harvard.edu}
}

@@

We should write an abstract here.

@@

Wooooo.

@@

\begin{thebibliography}{2}
  \bibitem{paxos}
    Paxos!

\end{thebibliography}

>>>>

\usepackage{xspace}
\newcommand\Motmot{\textsc{Motmot}\xspace}

@@

\title{Motmot: A Distributed Chat Protocol}

\numberofauthors{5}
%
\author{
  \alignauthor
  Carl Jackson \\
    \affaddr{Harvard University} \\
    \email{cjackson@college.harvard.edu}
  %
  \alignauthor
  Max Wang \\
    \affaddr{Harvard University} \\
    \email{max.wang@college.harvard.edu}
  %
  \alignauthor
  EJ Bensing \\
    \affaddr{Harvard University} \\
    \email{ebensing@college.harvard.edu}
  %
  \and
  \alignauthor
  Jeff Atwood \\
    \affaddr{Harvard University} \\
    \email{jatwood@college.harvard.edu}
  %
  \alignauthor
  Julie Hansbrough \\
    \affaddr{Harvard University} \\
    \email{jhansbrough@college.harvard.edu}
}

@@

\Motmot is a new distributed text chat protocol based on Paxos. Unlike previous
chat protocols like XMPP, OSCAR, and IRC, \Motmot provides guaranteed message
delivery, total message ordering, end-to-end encryption, peer authentication,
and message deniability.
% TODO: write more

@@

\section{libmotmot}

Guaranteed delivery and total message ordering are perhaps the most fundamental
chat features provided by \Motmot.  In order to obtain these properties, the
clients participating in a chat must reach a consensus concerning the reception
and order of chat events.  \Motmot assumes a benign failure model and uses a
variant of the Paxos consensus protocol \cite{paxos}, which is the core of its
client library \texttt{libmotmot}, in order to provide these guarantees.

\subsection{Design}

\subsection{Implementation}

\subsection{Testing}

\subsection{Lessons Learned}

\section{Discovery Server}

\section{Pidgin Plugin}

@@

\thebibliography{2}{
  \bibitem{paxlive}
    T. Chandra, R. Griesemer, and J. Redstone.
    Paxos made live---an engineering perspective.
    In \emph{Proc. 26th Symp. on Principles of Distributed Computing}, pp. 398-407, Aug. 2007.

  \bibitem{paxos}
    L. Lamport.
    The part-time parliament.
    \emph{ACM Transactions on Computer Systems}, 16(2):133-169, 1998.

  \bibitem{paxsimp}
    L. Lamport.
    Paxos made simple.
    \emph{ACM SIGACT News 32}, 4:18-25, Dec. 2001.

  \bibitem{rfc}
    P. Resnick, ed.
    Internet Message Format, RFC 2822.
    April 2001.
}
